LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment

### 2024-07-30 article/main.tex
place text after figures to ensure their availability in text links
fix figure layout
fix typos. rephrase unreadable paragraphs

The next step requires computing statistics on the corpus for each HLF:\@
\textbf{min}\~(the minimum value), \textbf{max}\~(the maximum value) and
\textbf{avg}\~(the mean).
These statistics allow writing an HLF prompt derived from each of our baseline
prompts.

The HLF prompts instruct the LLM to generate text with HLFs that comply with the
previously computed statistics.
The individual (per-HLF) instructions are all are part of the same HLF prompt.
The prompts are constructed using the Jinja2~\cite{jinja2} templates which are
located in the \texttt{\textlinkanon{https://github.com/koosie0507/llm-tst-consistency/tree/main/src/llm_tst_consistency/templates}{templates}}
directory of the source code used to run the experiment.
The instruction prompts corresponding to our two scenarios are
`\texttt{prompt\_1}' and `\texttt{prompt\_2}', respectively.
The rest of the templates in the directory are used to construct the individual
HLF instructions.

@@

Both variants of the second scenario quantify how similar the HLFs of the texts
generated by the LLM are to the corpus average \textit{because of} the HLF
instructions.
We assume that the LLM can generate text similar to text from the corpus when
instructed it with examples from the corpus.
The HLF instructions would remain as the possible cause for obtaining different
results from baseline.
The ID of the LLM is referenced throughout figures, tables and generally
throughout the rest of the paper.

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            ID          & Name                    & Parameters  & Context Size & Elo Score & License             \\ \toprule
            gpt         & OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
            gemini      & Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
            claude3     & Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
            llama3\_70b & Meta Llama 3-{}70B      & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
            command\_r  & Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                        &                         &             &              &           & with Acceptable Use \\
                        &                         &             &              &           & Addendum            \\ \bottomrule
        \end{tabular}%
    }
    \caption{Large Language Model Selection}\label{table-llm}
\end{table*}

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            LFTK ID         & Name                              & Family           & Domain           & Abstraction     & Style Level\footnotemark\\ \toprule
            t\_word         & total words                       & wordsent         & surface          & very concrete   & lexical                 \\
            t\_sent         & total sentences                   & wordsent         & surface          & very concrete   & syntactic               \\ \bottomrule
            n\_uverb        & total number of unique adjectives & partofspeech     & syntax           & concrete        & semantic                \\
            n\_uadj         & total number of unique adjectives & partofspeech     & syntax           & concrete        & syntactic               \\ \bottomrule
            simp\_ttr       & simple type token ratio           & typetokenratio   & lexico-semantics & regular         & pragmatic               \\
            a\_verb\_pw     & number of verbs per word          & partofspeech     & surface          & regular         & syntactic               \\ \bottomrule
            corr\_adj\_var  & corrected adjective variation     & lexicalvariation & lexico-semantics & abstract        & lexical                 \\
            corr\_verb\_var & corrected verb variation          & lexicalvariation & lexico-semantics & abstract        & lexical                 \\ \bottomrule
            fkgl            & Flesch-Kincaid grade level        & readformula      & surface          & highly abstract & pragmatic               \\
            a\_kup\_pw      & Kuperman age of aquisition        & worddiff         & lexico-semantics & highly abstract & lexical                 \\ \bottomrule
        \end{tabular}%
    }
    \caption{Handcrafted Linguistic Features}\label{table-hlf}
\end{table*}
\footnotetext{as described in the figure in~\cite{lugea2023stylistics}, chapter 1, page 7}

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            Name            & Task                     & Number of Samples & Content Type & Reference              & License           \\ \toprule
            Yelp Reviews    & Sentiment Classification & 50000             & Reviews      &~\cite{yelp2015neurips} & Yelp Dataset      \\
            (test split)    & Text Style Transfer      &                   &              &                        & License Agreement \\
                            & Text Classification      &                   &              &                        &                   \\ \midrule
            CNN / DailyMail & Summarization            & 11490             & News         &~\cite{cnndm2015}       & Apache 2.0        \\
            (test split)    & Question Answering       &                   & Stories      &~\cite{cnndm2017}       &                   \\
                            & Text Generation          &                   &              &                        &                   \\ \bottomrule
        \end{tabular}%
    }
    \caption{Source Datasets}\label{table-ds}
\end{table*}

@@

The text external to the CNN article corpus is an extract from the classic
\textit{The Life and Opinions of Tristram Shandy, Gentleman}, by Laurence
Sterne~\cite{sterne2003life}.
The text style is very dissimilar compared to news articles.
Its linguistic features are also very unlike the average values computed for the
CNN article corpus.
A text that is similarly divorced from the style and linguistic features of most
Yelp reviews is Oscar Wilde's \textit{Sonnet toLiberty}~\cite{wilde1909poems}.
Both texts are in the public domain and were obtained from Project
Gutenberg~\cite{gutenberg}.

@@

Determining whether the baseline results differ from the HLF-enhanced results is
a classic use case for the Kolmogorov-Smirnov~\cite{kolmogorov1933,smirnov1939}
test, as implemented in Scipy~\cite{2020SciPy-NMeth}.
We consider that the results are different for a resulting $p\_value \le 0.05$.

@@

\begin{table*}[htp]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var            & fkgl                    & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{623.16}}  & \textbf{\underline{24.74}} & \textbf{\underline{51.18}}  & \textbf{\underline{26.68}} & 0.06                      & -0.0                      & \textbf{\underline{0.46}} & \textbf{\underline{1.4}}   & 1.44                    & \textbf{\textit{-1.66}}   \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{1774.0}}  & \textbf{\underline{74.0}}  & \textbf{\underline{158.84}} & \textbf{\underline{81.2}}  & 0.2                       & -0.01                     & \textbf{\underline{1.88}} & \textbf{\underline{4.49}}  & 5.01                    & \textbf{\textit{-4.09}}   \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{985.86}}  & \textbf{\underline{34.52}} & \textbf{\underline{100.36}} & \textbf{\underline{53.39}} & \textbf{\underline{0.52}} & 0.05                      & \textbf{\underline{2.62}} & \textbf{\underline{4.68}}  & -4.17                   & \textbf{\textit{-2.43}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2990.5}}  & \textbf{\underline{106.5}} & \textbf{\underline{320.34}} & \textbf{\underline{159.1}} & \textbf{\underline{1.5}}  & 0.09                      & \textbf{\underline{7.24}} & \textbf{\underline{13.15}} & -12.65                  & \textbf{\textit{-7.13}}   \\ \midrule
            gpt $Diff\_N$         & \textbf{\underline{125.87}}  & 1.46                       & 10.95                       & 10.77                      & 0.02                      & -0.01                     & 0.71                      & 0.81                       & \textbf{\textit{-1.72}} & 0.43                      \\ \midrule
            gpt $Diff\_A$         & \textbf{\underline{327.0}}   & 3.0                        & 29.0                        & 27.0                       & 0.08                      & -0.01                     & 1.82                      & 2.24                       & \textbf{\textit{-5.72}} & 0.44                      \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{1024.78}} & \textbf{\underline{39.67}} & \textbf{\underline{81.58}}  & \textbf{\underline{41.46}} & \textbf{\underline{0.46}} & \textbf{\underline{0.03}} & \textbf{\underline{2.67}} & \textbf{\underline{3.78}}  & 1.4                     & \textbf{\underline{0.14}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{3132.5}}  & \textbf{\underline{120.5}} & \textbf{\underline{246.84}} & \textbf{\underline{132.2}} & \textbf{\underline{1.36}} & \textbf{\underline{0.06}} & \textbf{\underline{7.88}} & \textbf{\underline{11.21}} & 3.9                     & \textbf{\underline{1.03}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{459.45}}  & \textbf{\underline{17.78}} & \textbf{\underline{36.5}}   & \textbf{\underline{19.75}} & \textbf{\underline{0.12}} & \textbf{\underline{0.03}} & \textbf{\underline{1.43}} & \textbf{\underline{2.18}}  & 1.5                     & \textbf{\textit{-0.06}}   \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1363.5}}  & \textbf{\underline{54.0}}  & \textbf{\underline{106.5}}  & \textbf{\underline{60.5}}  & \textbf{\underline{0.36}} & \textbf{\underline{0.09}} & \textbf{\underline{4.33}} & \textbf{\underline{6.38}}  & 7.46                    & \textbf{\textit{-0.11}}   \\ \bottomrule
        \end{tabular}%
    }\caption{CNN Results}\label{table-prompt-1-cnn-dailymail}
\end{table*}

@@

\begin{figure*}[htp]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-command_r-cnn_dailymail/prompt_1-command_r-cnn_dailymail_t_word.png}
        \caption{Command-R+\\Total Words}\label{fig-command-r-t-word}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-gpt-cnn_dailymail/prompt_1-gpt-cnn_dailymail_fkgl.png}
        \caption{GPT\\Flesch-Kincaid Grade Level}\label{fig-gpt-fkgl}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-claude3-cnn_dailymail/prompt_1-claude3-cnn_dailymail_a_verb_pw.png}
        \caption[center]{Claude3\\Average Verbs per Word}\label{fig-llama-simp-ttr}
    \end{minipage}
\end{figure*}

@@

\begin{table*}[hpb]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var           & fkgl                       & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{718.49}}  & \textbf{\underline{24.13}} & \textbf{\underline{44.43}}  & \textbf{\underline{23.43}} & \textbf{\underline{0.4}}  & 0.03                      & 0.94                      & \textbf{\underline{0.77}} & 1.2                        & 0.07                      \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{2345.54}} & \textbf{\underline{90.18}} & \textbf{\underline{148.36}} & \textbf{\underline{63.6}}  & \textbf{\underline{1.18}} & 0.07                      & 1.36                      & \textbf{\underline{2.55}} & 3.33                       & 0.52                      \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{785.6}}   & \textbf{\underline{25.8}}  & \textbf{\underline{60.5}}   & \textbf{\underline{41.6}}  & \textbf{\underline{0.41}} & \textbf{\underline{0.05}} & \textbf{\underline{1.95}} & \textbf{\underline{2.67}} & -4.62                      & \textbf{\textit{-1.94}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2512.0}}  & \textbf{\underline{81.5}}  & \textbf{\underline{210.34}} & \textbf{\underline{125.7}} & \textbf{\underline{1.25}} & \textbf{\underline{0.09}} & \textbf{\underline{5.84}} & \textbf{\underline{8.05}} & -9.46                      & \textbf{\textit{-5.82}}   \\ \midrule
            gpt $Diff\_N$         & 47.8                         & 5.18                       & 6.13                        & -0.13                      & 0.02                      & 0.0                       & 0.05                      & 0.3                       & 3.06                       & -0.27                     \\ \midrule
            gpt $Diff\_A$         & 77.0                         & 12.5                       & 13.0                        & -4.0                       & 0.04                      & 0.0                       & -0.17                     & 0.77                      & 8.45                       & -0.16                     \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{263.51}}  & 5.35                       & \textbf{\underline{25.08}}  & \textbf{\underline{17.37}} & \textbf{\textit{-0.09}}   & -0.01                     & \textbf{\underline{1.74}} & \textbf{\underline{1.42}} & \textbf{\underline{10.46}} & \textbf{\underline{1.56}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{896.0}}   & 20.5                       & \textbf{\underline{86.0}}   & \textbf{\underline{60.6}}  & \textbf{\textit{-0.21}}   & -0.03                     & \textbf{\underline{5.45}} & \textbf{\underline{4.95}} & \textbf{\underline{31.29}} & \textbf{\underline{5.67}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{376.0}}   & \textbf{\underline{15.63}} & \textbf{\underline{38.63}}  & 15.74                      & \textbf{\underline{0.24}} & \textbf{\underline{0.06}} & 1.69                      & \textbf{\underline{2.91}} & 0.31                       & -0.3                      \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1088.5}}  & \textbf{\underline{45.0}}  & \textbf{\underline{113.0}}  & 41.0                       & \textbf{\underline{0.65}} & \textbf{\underline{0.18}} & 3.53                      & \textbf{\underline{8.56}} & 0.27                       & -0.68                     \\ \bottomrule
        \end{tabular}%
    }
    \caption{prompt 2 - CNN Results\\Input Outside Corpus}\label{table-prompt-2-cnn-dailymail} % chktex-file 8
\end{table*}

@@

\begin{figure*}[hpb]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail_t_word.png}
        \caption{GPT\\Total Words}\label{fig-p2-gpt-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail_simp_ttr.png}
        \caption{Command-R+\\Simple TTR}\label{fig-p2-command-r-simpttr}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Gemini\\Kuperman Age of Aquisition}\label{fig-p2-gemini-a-kup-pw}
    \end{minipage}
\end{figure*}

We finally look at the second variant of the second scenario of our experiment.
The hypothesis in this variant is that LLMs will generate text that exhibits
HLFs much closer to the target corpus average if the input text is from that
corpus.
The expectation is to see less significant results.
The results shown in Table~\ref{table-prompt-2-ifd-cnn-dailymail} contradict our
expectations outright.
The most surprising behaviour is exhibited for HLFs which are derived into more
concrete generation instructions, such as the total number of words.
This behaviour is highlighted in figure~\ref{fig-p2-ifd-gemini-twords}.
Additionally, we notice regressive behaviour for some models compared to the
previously explored results in figure~\ref{fig-p2-ifd-claude3-nuadj}.
Finally, the abstractness of the text generation instructions for certain HLFs
leads to the generated text not being compliant as exemplified in
figure~\ref{fig-p2-ifd-llama3-a-kup-pw}.

>>>>

The next step requires computing statistics on the corpus for each HLF:\@
\textbf{min}~(the minimum value), \textbf{max}~(the maximum value) and
\textbf{avg}~(the mean).
These statistics allow writing an HLF prompt derived from each of our baseline
prompts.

The HLF prompts instruct the LLM to generate text with HLFs that comply with the
previously computed statistics.
The individual (per-HLF) instructions are all part of the same HLF prompt.
The prompts are constructed using the Jinja2~\cite{jinja2} templates which are
located in the \texttt{\textlinkanon{https://github.com/koosie0507/llm-tst-consistency/tree/main/src/llm_tst_consistency/templates}{templates}}
directory of the source code used to run the experiment.
The instruction prompts corresponding to our two scenarios are
`\texttt{prompt\_1}' and `\texttt{prompt\_2}', respectively.
The rest of the templates in the directory are used to construct the individual
HLF instructions.

@@

Both variants of the second scenario quantify how similar the HLFs of the texts
generated by the LLM are to the corpus average \textit{because of} the HLF
instructions.
Working under the assumption that an LLM can generate text that is similar to an
example from the corpus, the presence of HLF instructions in the prompt would
remain among the few possible explanations were we to observe deviations from
the baseline.

@@

\begin{table*}[ht!]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            ID          & Name                    & Parameters  & Context Size & Elo Score & License             \\ \toprule
            gpt         & OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
            gemini      & Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
            claude3     & Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
            llama3\_70b & Meta Llama 3-{}70B      & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
            command\_r  & Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                        &                         &             &              &           & with Acceptable Use \\
                        &                         &             &              &           & Addendum            \\ \bottomrule
        \end{tabular}%
    }
    \caption{Large Language Model Selection}\label{table-llm}
\end{table*}

Throughout the remainder of this paper, we will reference individual LLMs by the
ID assigned to each one in Table~\ref{table-llm}.

@@

\begin{table*}[ht!]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            LFTK ID         & Name                              & Family           & Domain           & Abstraction     & Style Level\footnotemark\\ \toprule
            t\_word         & total words                       & wordsent         & surface          & very concrete   & lexical                 \\
            t\_sent         & total sentences                   & wordsent         & surface          & very concrete   & syntactic               \\ \bottomrule
            n\_uverb        & total number of unique adjectives & partofspeech     & syntax           & concrete        & semantic                \\
            n\_uadj         & total number of unique adjectives & partofspeech     & syntax           & concrete        & syntactic               \\ \bottomrule
            simp\_ttr       & simple type token ratio           & typetokenratio   & lexico-semantics & regular         & pragmatic               \\
            a\_verb\_pw     & number of verbs per word          & partofspeech     & surface          & regular         & syntactic               \\ \bottomrule
            corr\_adj\_var  & corrected adjective variation     & lexicalvariation & lexico-semantics & abstract        & lexical                 \\
            corr\_verb\_var & corrected verb variation          & lexicalvariation & lexico-semantics & abstract        & lexical                 \\ \bottomrule
            fkgl            & Flesch-Kincaid grade level        & readformula      & surface          & highly abstract & pragmatic               \\
            a\_kup\_pw      & Kuperman age of aquisition        & worddiff         & lexico-semantics & highly abstract & lexical                 \\ \bottomrule
        \end{tabular}%
    }
    \caption{Handcrafted Linguistic Features}\label{table-hlf}
\end{table*}
\footnotetext{as described in the figure in~\cite{lugea2023stylistics}, chapter 1, page 7}

@@

\begin{table*}[ht!]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            Name            & Task                     & Number of Samples & Content Type & Reference              & License           \\ \toprule
            Yelp Reviews    & Sentiment Classification & 50000             & Reviews      &~\cite{yelp2015neurips} & Yelp Dataset      \\
            (test split)    & Text Style Transfer      &                   &              &                        & License Agreement \\
                            & Text Classification      &                   &              &                        &                   \\ \midrule
            CNN / DailyMail & Summarization            & 11490             & News         &~\cite{cnndm2015}       & Apache 2.0        \\
            (test split)    & Question Answering       &                   & Stories      &~\cite{cnndm2017}       &                   \\
                            & Text Generation          &                   &              &                        &                   \\ \bottomrule
        \end{tabular}%
    }
    \caption{Source Datasets}\label{table-ds}
\end{table*}

@@

The text external to the CNN article corpus is an extract from the classic
\textit{The Life and Opinions of Tristram Shandy, Gentleman}, by Laurence
Sterne~\cite{sterne2003life}.
The text style is very dissimilar compared to news articles.
Its linguistic features are also very unlike the average values computed for the
CNN article corpus.
A text that is similarly divorced from the style and linguistic features of most
Yelp reviews is Oscar Wilde's \textit{Sonnet to Liberty}~\cite{wilde1909poems}.
Both texts are in the public domain and were obtained from Project
Gutenberg~\cite{gutenberg}.

@@

Determining whether the baseline results differ from the HLF-enhanced results is
a classic use case for the Kolmogorov-Smirnov
test~\cite{kolmogorov1933,smirnov1939}, as implemented in the
Scipy library~\cite{2020SciPy-NMeth}.
We consider that the results are different for a resulting $p\_value \le 0.05$.

@@

\begin{table*}[ht!]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var            & fkgl                    & a\_kup\_pw                \\
            \toprule
            claude3 $Diff_N$     & \textbf{\underline{623.16}}  & \textbf{\underline{24.74}} & \textbf{\underline{51.18}}  & \textbf{\underline{26.68}} & 0.06                      & -0.0                      & \textbf{\underline{0.46}} & \textbf{\underline{1.4}}   & 1.44                    & \textbf{\textit{-1.66}}   \\ \midrule
            claude3 $Diff_A$     & \textbf{\underline{1774.0}}  & \textbf{\underline{74.0}}  & \textbf{\underline{158.84}} & \textbf{\underline{81.2}}  & 0.2                       & -0.01                     & \textbf{\underline{1.88}} & \textbf{\underline{4.49}}  & 5.01                    & \textbf{\textit{-4.09}}   \\ \midrule
            gemini $Diff_N$      & \textbf{\underline{985.86}}  & \textbf{\underline{34.52}} & \textbf{\underline{100.36}} & \textbf{\underline{53.39}} & \textbf{\underline{0.52}} & 0.05                      & \textbf{\underline{2.62}} & \textbf{\underline{4.68}}  & -4.17                   & \textbf{\textit{-2.43}}   \\ \midrule
            gemini $Diff_A$      & \textbf{\underline{2990.5}}  & \textbf{\underline{106.5}} & \textbf{\underline{320.34}} & \textbf{\underline{159.1}} & \textbf{\underline{1.5}}  & 0.09                      & \textbf{\underline{7.24}} & \textbf{\underline{13.15}} & -12.65                  & \textbf{\textit{-7.13}}   \\ \midrule
            gpt $Diff_N$         & \textbf{\underline{125.87}}  & 1.46                       & 10.95                       & 10.77                      & 0.02                      & -0.01                     & 0.71                      & 0.81                       & \textbf{\textit{-1.72}} & 0.43                      \\ \midrule
            gpt $Diff_A$         & \textbf{\underline{327.0}}   & 3.0                        & 29.0                        & 27.0                       & 0.08                      & -0.01                     & 1.82                      & 2.24                       & \textbf{\textit{-5.72}} & 0.44                      \\ \midrule
            command\_r $Diff_N$  & \textbf{\underline{1024.78}} & \textbf{\underline{39.67}} & \textbf{\underline{81.58}}  & \textbf{\underline{41.46}} & \textbf{\underline{0.46}} & \textbf{\underline{0.03}} & \textbf{\underline{2.67}} & \textbf{\underline{3.78}}  & 1.4                     & \textbf{\underline{0.14}} \\ \midrule
            command\_r $Diff_A$  & \textbf{\underline{3132.5}}  & \textbf{\underline{120.5}} & \textbf{\underline{246.84}} & \textbf{\underline{132.2}} & \textbf{\underline{1.36}} & \textbf{\underline{0.06}} & \textbf{\underline{7.88}} & \textbf{\underline{11.21}} & 3.9                     & \textbf{\underline{1.03}} \\ \midrule
            llama3\_70b $Diff_N$ & \textbf{\underline{459.45}}  & \textbf{\underline{17.78}} & \textbf{\underline{36.5}}   & \textbf{\underline{19.75}} & \textbf{\underline{0.12}} & \textbf{\underline{0.03}} & \textbf{\underline{1.43}} & \textbf{\underline{2.18}}  & 1.5                     & \textbf{\textit{-0.06}}   \\ \midrule
            llama3\_70b $Diff_A$ & \textbf{\underline{1363.5}}  & \textbf{\underline{54.0}}  & \textbf{\underline{106.5}}  & \textbf{\underline{60.5}}  & \textbf{\underline{0.36}} & \textbf{\underline{0.09}} & \textbf{\underline{4.33}} & \textbf{\underline{6.38}}  & 7.46                    & \textbf{\textit{-0.11}}   \\ \bottomrule
        \end{tabular}%
    }\caption{CNN Results}\label{table-prompt-1-cnn-dailymail}
\end{table*}

@@

\begin{figure*}[ht!]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-command_r-cnn_dailymail/prompt_1-command_r-cnn_dailymail_t_word.png}
        \caption{Command-R+\\Total Words}\label{fig-command-r-t-word}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-gpt-cnn_dailymail/prompt_1-gpt-cnn_dailymail_fkgl.png}
        \caption{GPT\\Flesch-Kincaid Grade Level}\label{fig-gpt-fkgl}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-claude3-cnn_dailymail/prompt_1-claude3-cnn_dailymail_a_verb_pw.png}
        \caption[center]{Claude3\\Average Verbs per Word}\label{fig-llama-simp-ttr}
    \end{minipage}
\end{figure*}

@@

\begin{table*}[ht!]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var           & fkgl                       & a\_kup\_pw                \\
            \toprule
            claude3 $Diff_N$     & \textbf{\underline{718.49}}  & \textbf{\underline{24.13}} & \textbf{\underline{44.43}}  & \textbf{\underline{23.43}} & \textbf{\underline{0.4}}  & 0.03                      & 0.94                      & \textbf{\underline{0.77}} & 1.2                        & 0.07                      \\ \midrule
            claude3 $Diff_A$     & \textbf{\underline{2345.54}} & \textbf{\underline{90.18}} & \textbf{\underline{148.36}} & \textbf{\underline{63.6}}  & \textbf{\underline{1.18}} & 0.07                      & 1.36                      & \textbf{\underline{2.55}} & 3.33                       & 0.52                      \\ \midrule
            gemini $Diff_N$      & \textbf{\underline{785.6}}   & \textbf{\underline{25.8}}  & \textbf{\underline{60.5}}   & \textbf{\underline{41.6}}  & \textbf{\underline{0.41}} & \textbf{\underline{0.05}} & \textbf{\underline{1.95}} & \textbf{\underline{2.67}} & -4.62                      & \textbf{\textit{-1.94}}   \\ \midrule
            gemini $Diff_A$      & \textbf{\underline{2512.0}}  & \textbf{\underline{81.5}}  & \textbf{\underline{210.34}} & \textbf{\underline{125.7}} & \textbf{\underline{1.25}} & \textbf{\underline{0.09}} & \textbf{\underline{5.84}} & \textbf{\underline{8.05}} & -9.46                      & \textbf{\textit{-5.82}}   \\ \midrule
            gpt $Diff_N$         & 47.8                         & 5.18                       & 6.13                        & -0.13                      & 0.02                      & 0.0                       & 0.05                      & 0.3                       & 3.06                       & -0.27                     \\ \midrule
            gpt $Diff_A$         & 77.0                         & 12.5                       & 13.0                        & -4.0                       & 0.04                      & 0.0                       & -0.17                     & 0.77                      & 8.45                       & -0.16                     \\ \midrule
            command\_r $Diff_N$  & \textbf{\underline{263.51}}  & 5.35                       & \textbf{\underline{25.08}}  & \textbf{\underline{17.37}} & \textbf{\textit{-0.09}}   & -0.01                     & \textbf{\underline{1.74}} & \textbf{\underline{1.42}} & \textbf{\underline{10.46}} & \textbf{\underline{1.56}} \\ \midrule
            command\_r $Diff_A$  & \textbf{\underline{896.0}}   & 20.5                       & \textbf{\underline{86.0}}   & \textbf{\underline{60.6}}  & \textbf{\textit{-0.21}}   & -0.03                     & \textbf{\underline{5.45}} & \textbf{\underline{4.95}} & \textbf{\underline{31.29}} & \textbf{\underline{5.67}} \\ \midrule
            llama3\_70b $Diff_N$ & \textbf{\underline{376.0}}   & \textbf{\underline{15.63}} & \textbf{\underline{38.63}}  & 15.74                      & \textbf{\underline{0.24}} & \textbf{\underline{0.06}} & 1.69                      & \textbf{\underline{2.91}} & 0.31                       & -0.3                      \\ \midrule
            llama3\_70b $Diff_A$ & \textbf{\underline{1088.5}}  & \textbf{\underline{45.0}}  & \textbf{\underline{113.0}}  & 41.0                       & \textbf{\underline{0.65}} & \textbf{\underline{0.18}} & 3.53                      & \textbf{\underline{8.56}} & 0.27                       & -0.68                     \\ \bottomrule
        \end{tabular}%
    }
    \caption{prompt 2 - CNN Results\\Input Outside Corpus}\label{table-prompt-2-cnn-dailymail} % chktex-file 8
\end{table*}

@@

\begin{figure*}[ht!]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail_t_word.png}
        \caption{GPT\\Total Words}\label{fig-p2-gpt-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail_simp_ttr.png}
        \caption{Command-R+\\Simple TTR}\label{fig-p2-command-r-simpttr}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Gemini\\Kuperman Age of Aquisition}\label{fig-p2-gemini-a-kup-pw}
    \end{minipage}
\end{figure*}

We finally look at the second variant of the second scenario of our experiment.
The hypothesis in this scenario variant was that the baseline would exhibit HLFs
that are much closer to the target corpus average if the input text is from that
corpus.
The expectation is to see fewer significant HLF results and that, as a rule of
thumb, HLF results are closer to the baseline in all cases.
The results shown in Table~\ref{table-prompt-2-ifd-cnn-dailymail} contradict our
expectations outright.
The most surprising behaviour is exhibited for HLFs which are derived into more
concrete generation instructions, such as the total number of words.
This behaviour is highlighted in figure~\ref{fig-p2-ifd-gemini-twords}.
Additionally, we notice regressive behaviour for some models compared to the
previously explored results in figure~\ref{fig-p2-ifd-claude3-nuadj}.
Finally, the abstractness of the text generation instructions for certain HLFs
leads to the generated text not being compliant as exemplified in
figure~\ref{fig-p2-ifd-llama3-a-kup-pw}.
